Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-15 VMCAI-revised-version/final.tex
effectivity

\begin{theorem}\label{indec WSTS}
Resilience for post-effective $\omega^2$-WSTS with strong compatibility and for upward closed set $\Safe$ is undecidable.
\end{theorem}

\begin{proof}
Indeed, consider the family $\{ f_j: \N^2 \to \N^2\}$ of 
increasing recursive functions from \cite{FMP-ic04} defined as

@@

\begin{proof}
\alain{pas facile à lire, à réécrire et à repenser}
This stems from the fact that it is undecidable for Minsky machines with more than one counter,
which can be simulated by WSTS.
Indeed, {\sc Resilience} is undecidable for Minsky machine with at least $3$ counters.
This is due to the undecidability of $2$-counter Minsky machine termination~\cite{Min61,Min67}.
From a $2$-counter Minsky machine $M$, one can construct a $3$-counter Minsky machine $M'$ 
such that machine $M$ terminates for all inputs iff machine $M'$ can reach $(0,0,0)$ from any input with at least $1$ on its third counter. We build $M'$ to simulate $M$ until it reaches a control-state indicative of termination, then lower the first two counters until they reach $0$, then, and only then, finally lower the third counter until it reaches $0$.
Remark that in the construction, from any input with at least $1$ on its third counter, it is not possible to reach $(1,0,0)$, $(0,1,0)$ or $(1,1,0)$.
Based on this construction, the problem of deciding whether the downward closed set $\downarrow (1,1,0)$ is reachable in a $3$-counter Minsky machine
from any input with at least $1$ on its third counter is undecidable. 
Hence {\sc Resilience} is undecidable for Minsky machines.

>>>>

\begin{theorem}\label{indec WSTS}
Resilience for post-effective $\omega^2$-WSTS with strong compatibility and for upward closed set $\Safe$ is undecidable.
\end{theorem}
\alain{peut-on ajouter des hypothèses d'effectivity ? peut-on montrer que l'exemple n'est pas pred effectif ? l'exemple est-il  ideal-effective (oui pour les propriétes 1 et 2 mais 3 ?)? on voit que l'exemple n'est pas completion-post-effective vu le theoreme qui suit}
\begin{proof}
Indeed, consider the family $\{ f_j: \N^2 \to \N^2\}$ of 
increasing recursive functions from \cite{FMP-ic04} defined as

@@

\begin{proof}
\alain{est-ce sur qu'on peut rajouter l'hypothese "ideal-effective" . preuve pas facile à lire, à réécrire et à repenser}
This stems from the fact that it is undecidable for Minsky machines with more than one counter,
which can be simulated by WSTS.
Indeed, {\sc Resilience} is undecidable for Minsky machine with at least $3$ counters.
This is due to the undecidability of $2$-counter Minsky machine termination~\cite{Min61,Min67}.
From a $2$-counter Minsky machine $M$, one can construct a $3$-counter Minsky machine $M'$ 
such that machine $M$ terminates for all inputs iff machine $M'$ can reach $(0,0,0)$ from any input with at least $1$ on its third counter. We build $M'$ to simulate $M$ until it reaches a control-state indicative of termination, then lower the first two counters until they reach $0$, then, and only then, finally lower the third counter until it reaches $0$.
Remark that in the construction, from any input with at least $1$ on its third counter, it is not possible to reach $(1,0,0)$, $(0,1,0)$ or $(1,1,0)$.
Based on this construction, the problem of deciding whether the downward closed set $\downarrow (1,1,0)$ is reachable in a $3$-counter Minsky machine
from any input with at least $1$ on its third counter is undecidable. 
Hence {\sc Resilience} is undecidable for Minsky machines.
